Multilocus Genotype And Mycelial Compatability Group Assessment

### 2017-07-11 doc/RMD/mlg-mcg.Rmd
update MCG barplot

```{r barplots, fig.width = 5, fig.height = 10}
mcg_graph <- mcgs %>% 
  filter(Samples > 1) %>%
  gather(type, count, MLGs, Samples, -Evenness) %>%
  arrange(desc(type), count) %>%
  rename(Type = type) %>%
  mutate(MCG = forcats::fct_inorder(MCG, ordered = TRUE)) %>%
  ggplot(aes(x = MCG, y = count, group = Type, fill = Type, alpha = Evenness)) +
  geom_col(aes(width = ifelse(Type == "MLGs", 0.5, 0.85)), color = "black", position = "identity") +
  # annotate(geom = "text", x = 18, y =35, 
  #          label = sprintf("Mean Evenness: %.3f", mean(mcgs$Evenness, na.rm = TRUE))) +
  scale_fill_manual(values = c("black", "white")) +
  scale_y_continuous(expand = c(0, 2)) +
  theme_minimal(base_size = 16, base_family = "Helvetica") +
  coord_flip() +
  theme(panel.grid.major.y = element_blank()) +
  theme(legend.box.just = "left") +
  theme(legend.box.margin = unit(c(0, 0.55, 11, 0), "lines")) +
  theme(legend.box.background = element_rect(fill = NA, color = "black")) +
  # theme(legend.box = "horizontal") +
  theme(aspect.ratio = 2) +
  labs(list(
    alpha = "MLG\nEvenness"
  ))

@@

vp1 <- grid::viewport(width = 0.25, height = 0.4, x = 0.795, y = 0.64, just = c("center", "top"))
mcg_graph <- mcg_graph + theme(legend.position = c(.789, .585))

pdf(file.path(PROJHOME, "results/figures/publication/Figure1Z.pdf"), width = 5, height = 10)
print(mcg_graph)
print(even, vp = vp1)
dev.off()

print(mcg_graph)
print(even, vp = vp1)
```

>>>>

```{r barplots, fig.width = 10, fig.height = 5}
mcg_graph <- mcgs %>% 
  filter(Samples > 1) %>%
  gather(type, count, MLGs, Samples, -Evenness) %>%
  arrange(desc(type), desc(count)) %>%
  rename(Type = type) %>%
  mutate(MCG = forcats::fct_inorder(MCG, ordered = TRUE)) %>%
  ggplot(aes(x = MCG, y = count, group = Type, fill = Type, alpha = Evenness)) +
  geom_col(aes(width = ifelse(Type == "MLGs", 0.5, 0.85)), color = "black", position = "identity") +
  # annotate(geom = "text", x = 18, y =35, 
  #          label = sprintf("Mean Evenness: %.3f", mean(mcgs$Evenness, na.rm = TRUE))) +
  scale_fill_manual(values = c("black", "white")) +
  scale_y_continuous(expand = c(0, 2)) +
  theme_minimal(base_size = 16, base_family = "Helvetica") +
  # coord_flip() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  theme(panel.grid.major.x = element_blank()) +
  theme(panel.grid.major.y = element_line(color = "grey50")) +
  theme(panel.grid.minor.y = element_line(color = "grey70")) +
  theme(legend.box.just = "top") +
  theme(legend.box.margin = unit(c(0, 6.55, 0, 0), "lines")) +
  theme(legend.box.background = element_rect(fill = "white", color = "black")) +
  theme(legend.box = "horizontal") +
  theme(aspect.ratio = 1/2) +
  labs(list(
    alpha = "MLG\nEvenness"
  ))

@@

vp1 <- grid::viewport(width = 0.25, height = 0.4, x = 1, y = 0.975, just = c("right", "top"))
mcg_graph <- mcg_graph + theme(legend.position = c(.763, .75))

print(mcg_graph)
print(even, vp = vp1)

if (!interactive()){
  pdf(file.path(PROJHOME, "results/figures/publication/Figure1Z.pdf"), width = 10, height = 5)
  print(mcg_graph)
  print(even, vp = vp1)
  dev.off()
}
```
